---
title: "Graph based functions"
author: "Jonathan Bourne"
date: "11 September 2017"
output: html_document
---

Just under 20 node attacks an hour


Create a function that takes two networks and finds the jaccard similarity after a cascade/attack. It is interesting to know is the proportionally loaded networks collapse in a more simmilar way to each other than to the actual line limits.


The goal of this script is to create graph objects that contain all the necessary information resulting in the manipulation of graphs performing most of the cleaning.

The hope is that this will make the processes and code more simple and easier to understand


This work is simmilar to Wang et al "An Electrical Betweenness approach for vulnerability assement of power grids considering the capacity of generators and load"

Changing the assement metric to loss of load and removing 20% of nodes e.g about 200.




https://www.forbes.com/sites/katevinton/2014/07/10/hacking-gets-physical-utilities-at-risk-for-cyber-attacks/#5131cd657af9

#some isreali dudes did something on the american grid
https://www.nature.com/articles/nphys2727


#Doctorate includes at least part on cyber attacks on grids
http://digitalcommons.uri.edu/cgi/viewcontent.cgi?article=1279&context=oa_diss

#Contact details charging team
01926 654633 or email charging.enquires@nationalgrid.com

I should change the graph so all information is encoded into it as graph attributes.


A stress metric or loading metric, that gives some sort of measure of how close the network is to having black outs would be really useful, that would help identify nodes that increase stress but don't actually cause any blackouts themselves. Preperation nodes

#next week

each node and each edge removed
re-do figures
get extreme node list - can save and dump files

small hand example
simple starter explnation





#Setup Chunk

```{r}
setwd("/home/jonno/Create_ETYS_network/SubCode")
source("Setup.R")

source("LoadData2.R")

LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Upgrade Report" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")

```


#Change basic graph line limits

The line limits for 4 edges are such that they are over the limit in the DC power loads under normal operation both in my calculuations and those of the national grid. These line limits are lower than the average for that voltage class. I am going to increase the line limit to ensure that each line has not exceeded it's limit under the dc calculations of normal operations.
The solution has already been put in the loading data phase and this code is kept for methodical clarity
```{r}

# g <- CalcOverLimit(gbase)
# 
# fixedge <- g %>% as_data_frame %>%
#   mutate(over.limit = Link.Limit < abs(PowerFlow))
# 
# Voltageav <- fixedge %>%
#   filter(Link.Limit !=max(Link.Limit)) %>%#simulated links have extremly high limits and should be ignored
#   group_by(Voltage) %>%
#   summarise(median = median(Link.Limit),
#             mean = mean(Link.Limit))
# 
# Voltage132 <- fixedge %>%
#   filter(Link.Limit !=max(Link.Limit), Voltage == 132) %>%
#   group_by(Link.Limit) %>%
#   summarise(counts = n())

```



#produce subgraph k jumps away from named node

```{r}
KNearestNodes(gbase, "TAUN4A", 2) %>% induced_subgraph(gbase, .) %>% plot
```

#Create a Hand solvable power flow



```{r}
testmat <- matrix(c(0,1,-1,0,-1,1,-1,0,1), nrow = 3, byrow = T)
#Connector nodes can produce the maximum power allowed by the power limit of thier connecting lines
Southwest <- str_split("EXET40 ALVE4B ALVE4A TAUN4A TAUN4B ABHA4B ABHA4A LAGA40 LAND4A LAND4B INDQ40", pattern = " ", simplify = T) 

Southwestg <- CreateSubgraph(gbase, Southwest[8:11] )

get.vertex.attribute(Southwestg)
Southwestg %>% plot
dev.copy(pdf,file.path(FiguresFolder, 'exampleIndianQueens.pdf'))
dev.off()

SlackRef <-"LAND4A"# "EXET40"
AZero <- CreateTransmission(Southwestg, "Link")
A <- AZero[,colnames(AZero)!=SlackRef, drop = FALSE]
C <- LinePropertiesMatrix(Southwestg) %>% round(., 1)

B <- t(A) %*% C %*% A
  
InjectionVector <- get.vertex.attribute(Southwestg, "BalencedPower")[get.vertex.attribute(Southwestg, "name")!=SlackRef] %>%
  round(., 1)

Power <- C %*% A %*% solve(B, InjectionVector) %>% round(.,1)

PrintLatexMatrix <- function(df, name, Folder = MatricesFolder){
  xtable(df,align=rep("",ncol(df)+1)) %>%
  print(., file = file.path(Folder, paste0(name, ".txt")), floating=FALSE, tabular.environment="bmatrix", 
  hline.after=NULL, include.rownames=FALSE, include.colnames=FALSE)

}

rownames(A) <- rownames(A) %>% gsub("-1", "",.)
xtable(A, format = "latex",label = "tab:A", caption = "Line transmission matrix")  %>%
  print(., file = file.path(MatricesFolder, "A.txt"))

xtable(B, format = "latex",label = "tab:B", caption = "The susceptance matrix") %>%
  print(., file = file.path(MatricesFolder, "B.txt"))

xtable(solve(B), format = "latex",label = "tab:Binv", caption = "The impedance matrix") %>%
  print(., file = file.path(MatricesFolder, "Binv.txt"))

xtable(C %*% A %*% solve(B), format = "latex",label = "tab:PTDF", caption = "The PTDF") %>%
  print(., file = file.path(MatricesFolder, "PTDF.txt"))
  
rownames(C) <- rownames(C) %>% gsub("-1", "",.)
#colnames(C) <-colnames(rep(" ", ncol(C)))# colnames(C) %>% gsub("-1", "",.)
xtable(C, format = "latex",label = "tab:C", caption = "Line properties matrix") %>% 
  print(., file = file.path(MatricesFolder, "C.txt"),include.colnames = FALSE)

PrintLatexMatrix(A, "Amat")

PrintLatexMatrix(B, "Bmat")

PrintLatexMatrix(C, "Cmat")

PrintLatexMatrix(t(A), "AmatTrans")

PrintLatexMatrix(Power, "Powermat")

PrintLatexMatrix(C %*% A %*% solve(B), "PTDFmat")

Inject <- get.vertex.attribute(Southwestg, "BalencedPower") %>%
  round(., 1) %>% as.matrix()

colnames(Inject) <-"Power"
rownames(Inject) <-  get.vertex.attribute(Southwestg, "name")

  xtable(Inject, format = "latex",label = "tab:Inject", caption = "Power balence") %>% 
    print(., file = file.path(MatricesFolder, "Inject.txt"))

  InjectionVector %>% as.matrix %>%
PrintLatexMatrix(., "Injmat")
  
 LinkLimits <- data_frame(name = get.edge.attribute(Southwestg, "name"), Power = Power[,1], Limits = get.edge.attribute(Southwestg, "Link.Limit")) 
 
 LinkLimits %>% 
   mutate('Over Limit? ' = Power> Limits) %>%
   xtable(., format = "latex",label = "tab:PowerRes", caption = "Result of power flow equations") %>% 
  print(., file = file.path(MatricesFolder, "PowerRes.txt"))
   
    
```

#Implementing net-ability and entropic degree from Bompard et al 2009

The netability score must be calculated using the ORIGINAL number of generator and demand nodes on the network, this is not possible using my current setup as all the nodes that are seperated from the network are removed to reducing the computational complexity.

However as Attack the grid produces a list of all the networks, the data of the original network can be used to calculate the netability of all subsequent networks.

It might be interesting to rank the link limits and then select links by limit rank... or reverse rank?
```{r}
PTDF <- C %*% A %*% solve(B)
Imp <- solve(B)
ElecDist <- ElectricalDistance(Imp)

InjectionVector <- get.vertex.attribute(Southwestg, "BalencedPower")[get.vertex.attribute(Southwestg, "name")!=SlackRef]

CapacityMatrix <- TransferCapacity(Southwestg, PTDF)

  Numerator <- CapacityMatrix/ElecDist
  
  Numerator[!is.finite(Numerator)] <- 0
  
  Denominator <- sum(InjectionVector>0)*sum(InjectionVector<0)
  
  NetAb <- sum(Numerator)/Denominator


Net_Ability(Southwestg)

wholgridNet<- Net_Ability(gbase,SlackRef)

test <- ElectricalDistance(gbase)

```

#Visualising metrics

```{r}
MetricVisualisation <- bind_rows(data_frame(values = degree(gbase), metric = "degree"),
                  data_frame(values = EntropicDegree(gbase), metric = "EntropicDegree"),
                  data_frame(values = betweenness(gbase)+1, metric = "Betweeness")
                  ) %>%
  filter(is.finite(values))

ggPowerLaw(MetricVisualisation)

ggsave(file.path(FiguresFolder, "MetricVisualisation.eps"))
```


#Power Law tests

```{r}



```


#Test various fixed strategies
```{r}
set.seed(15)
DeleteNodes <- RandomAttack(gbase, Target = "Nodes", Number = vcount(gbase))
DeleteNodes <- DegreeAttack(gbase, Number = vcount(gbase))
DeleteNodes <- BetweenessAttack(gbase, Target = "Nodes", Number = vcount(gbase))
DeleteNodes <- EntropicDegreeAttack(gbase, Target = "Nodes", Number = vcount(gbase))

DeleteEdges <-RandomAttack(gbase, Target = "Edges", Number = ecount(gbase))

FixedNodes <- quo(FixedStrategyAttack(g, DeleteNodes))
FixedEdges <- quo(FixedStrategyAttack(g, DeleteEdges, Target = "Edges"))

g <- PowerFlow(gbase, "FECK40")

testattack <- AttackTheGrid(list(list(g)), FixedNodes, MinMaxComp = 0, TotalAttackRounds = 10, CascadeMode = TRUE)

#extract the number of nodes in the last of each list, precursor to finding the deleted node
 NodesTargeted(testattack)

#dataframe of load profiles
LoadProfiles <- 1:10 %>% map(
  ~data_frame(name = get.vertex.attribute(g, "name"), Demand=  get.vertex.attribute(g, "Demand" )) %>%
    setNames(c("name", paste0("Demand", .x))) ) %>%
  Reduce(function(...) merge(..., by='name', all.x=TRUE), .)

#attack across mutliple load profiles... in this case the load profile is the same
setwd(basewd)
testres <- MultiAttack(g, LoadProfiles,
            AttackStrategy = RandomAttack,
                           Type = "Fixed",
                           MinMaxComp = 0.0, 
                           TotalAttackRounds = 15,
                           Target = "Nodes",
                           CascadeMode = FALSE,
                           SaveGridList = "test",
                           cores = 1)


test <- ExtractNetworkStats(testattack)
ExtractNetworkStats(wtf)

Alphalevels <- c(1.05, 1.20, 1.5, 2, 3, 5) 

#a list of networks that have proportional loading
AlphaNets <-Alphalevels  %>% map(~
  ProportionalLimits(gbase, alpha = .x)
) %>% setNames(paste0("Alpha", Alphalevels))
  

AlphaNets %>% map(~get.edge.attribute(.x, "Link.Limit")) %>%
  setNames(paste0("Alpha", Alphalevels)) %>%
  bind_cols()


g2 <- ProportionalLimits(g)

test <- data_frame(base = get.edge.attribute(g, "Link.Limit"), alpha1.05 = get.edge.attribute(g2, "Link.Limit"))


test<- 1:2%>%
  map(~MultiAttack(list(g2, gbase)[[.x]], LoadProfiles,
                           AttackStrategy = RandomAttack,
                           Type = "Fixed",
                           MinMaxComp = 0.0, 
                           TotalAttackRounds = 15,
                           Target = "Nodes",
                           CascadeMode = TRUE,
                           SaveGridList =c("Alpha105", "Base")[.x],
                           cores = 7)
    )


# Error in { : task 2 failed - "Invalid vertex names" 
#I think this can only be debugged by adding in a "fixed" random node removal. then I can see which one is causing the error and find out why it is happening
setwd(basewd)
testres <- MultiAttack(g2, LoadProfiles,
            AttackStrategy = RandomAttack,
                           Type = "Fixed",
                           MinMaxComp = 0.0, 
                           TotalAttackRounds = 15,
                           Target = "Nodes",
                           CascadeMode = FALSE,
                           SaveGridList = "test",
                           cores = 7)

```


```{r}
#going to add on a new node then remove it as the slackbuss

g <- Southwestg
SlackRef <-  "LAND4A"

testg <- add_vertices(Southwestg, 1, name = "Slack", Demand = 50, Generation = 0, BalencedPower = -50) %>%
  add_edges(c(1, vcount(.), 2, vcount(.))) %>%
  BalencedGenDem(., "Demand", "Generation")

test <- ImpPTDF(g, SlackRef)

a <-ElectricalDistance(test$Imp)

rank.a <- a
rank.a[] <- rank(-a, ties.method = "random")
colnames(rank.a) <- rownames(rank.a)<- get.vertex.attribute(g)$name[get.vertex.attribute(g)$name!=SlackRef ]

adjmat <- rank.a <=ecount(g)
g2 <-a * adjmat 

g2 <- graph_from_adjacency_matrix(g2, weighted = TRUE , mode = "undirected") 

betweenness(g2) %>% density %>% plot

data_frame(name = get.vertex.attribute(g2, "name"), betweeness = betweenness(g2)) %>%
  arrange(desc(betweeness))

delete.vertices(simplify(g2), degree(g2)==0) %>% betweenness %>% table

g3 <- BalencedGenDem(g2, "Demand", "Generation")

g2 %>% plot

a1 <- a
rank.a1 <- rank.a



```


#Delete each node see what happens

This code cycles through all nodes and edges and measures the effect of the GCfract and PowerGen for a single outage.

```{r}
EdgeNodeDeleteion <- c("Nodes", "Edges") %>% map_df(~{

  Target = .x
  Number <- ifelse(Target == "Nodes", vcount(gbase), ecount(gbase))
  
    DeleteNodes <- RandomAttack(gbase, Target = Target, Number = Number)
    Out <- DeleteNodes %>% 
      map2_df(.x = ., .y = Target, ~{
      
       DeleteNodes <- .x
       #FixedNodes <- quo(FixedStrategyAttack(g, DeleteNodes))
      
       FixedNodes <- quo(FixedStrategyAttack(g, DeleteNodes, UQS(list(Target = .y))))
       
       AttackTheGrid(list(list(gbase)), 
                     FixedNodes, 
                     MinMaxComp = 0, 
                     TotalAttackRounds = 1, 
                     CascadeMode = TRUE) %>% 
        ExtractNetworkStats(.) %>%
        mutate(Deleted = .x,
               Type = .y)
        
      }
    )

  }
)

setwd(basewd)
saveRDS(EdgeNodeDeleteion, "CheckAllEdgeNodes.rds")

#EdgeNodeDeleteion <- readRDS("CheckAllEdgeNodes.rds")

#Correction for load removed when Nodes are taken out?
test <- EdgeNodeDeleteion %>% 
  mutate(Nodeslost=  max(TotalNodes)-TotalNodes ,
         Edgeslost = max(TotalEdges)-  TotalEdges,
         Blackout = (max(PowerGen)-PowerGen)/max(PowerGen)) %>%
  filter(NodesAttacked == 1) 

test %>%
  ggplot(.,aes(Nodeslost)) + geom_histogram() +
  facet_grid(.~Type)
  

test %>%
  ggplot(.,aes(Edgeslost)) + 
  geom_histogram() +
  facet_grid(.~Type)

test %>%
  ggplot(.,aes(Blackout)) + geom_density() +
  facet_grid(.~Type)+ scale_x_log10()

test %>%
  ggplot(aes(x = Edgeslost, Blackout))+ geom_point()

```


#Node collapse

I think that dead islands are a major cause of grid collapse.

In certain cases you can see that edges get removed in cascade even when they are not close to the nodes/edges that were have been removed in the previous iteration, this finding is also seen by yang et al

```{r}
set.seed(1234)

input <- c(TRUE,FALSE)
g <- PowerFlow(gbase, "FECK40")
  Nodesims <- input %>% map(~{ 
    MonteCarloAttack(g, 
                           simulations = 100,
                           AttackStrategy = RandomAttack,
                           Type = "Fixed",
                           MinMaxComp = 0.0, 
                           TotalAttackRounds = 150,
                           Target = "Nodes",
                           CascadeMode = .x,
                           cores = 3)
    

    }
   ) %>% set_names(paste0("v.", input))
  
  
  Nodesims <- input %>% map(~{ 
    MonteCarloAttack(g, 
                           simulations = 100,
                           AttackStrategy = RandomAttack,
                           Type = "Fixed",
                           MinMaxComp = 0.0, 
                           TotalAttackRounds = 150,
                           Target = "Nodes",
                           CascadeMode = .x,
                           cores = 3)
    

    }
   ) %>% set_names(paste0("v.", input))

setwd(basewd)
saveRDS(Nodesims, "100simulationsRandomAttackto150Nodes.rds")
#Nodesims <- readRDS( "100simulationsRandomAttackto150Nodes.rds" )

SummaryofGC <- Nodesims %>%
    modify_depth(., 1, keep, is.data.frame ) %>%
  flatten %>%
  bind_rows() %>% 
  SummariseMonteCarlo %>%
  mutate(PercNum = NodesAttacked/958)


NodeCollapse <- rbind(SummaryofGC %>%
  select(PercNum, mean, Cascade, GC05, GC95) %>% mutate(type = "Giant componant size reduction"),
SummaryofGC %>% 
  select(PercNum, mPGfract, Cascade, PG05, PG95) %>% mutate(type = "Blackout size") %>%
  rename(mean = mPGfract, GC05 = PG05, GC95 = PG95)
) %>% mutate(Target = "Node")

#Plot for the above is made in the next data chunk where edges are also included.


PNodeDens <-  Nodesims %>%
    modify_depth(., 1, keep, is.data.frame ) %>%
  flatten %>%
  bind_rows() %>%
  mutate(PercNum = round(NodesAttacked*100/958),
            LoadDrop = (first(GridLoading)-GridLoading)/first(GridLoading))

test <- PNodeDens %>% group_by(Cascade, NodesAttacked)%>% 
  summarise(mean = mean(Blackout),
            median = median(Blackout))

x=c(1:958)/958
target=c(1:15)/100
targnodes <- target %>% map_dbl(~which(abs(x-.x)==min(abs(x-.x))))


PNodeDens %>%
  filter(NodesAttacked %in% targnodes) %>%
  mutate(  PercAttacked= fct_rev(as_factor(paste0(PercNum, "%"))))  %>%
  ggplot(aes(y = PercAttacked)) +
  geom_density_ridges(aes(x = Blackout, fill = Cascade), alpha = 0.5) +
  labs(x = "Blackout size as Percentage of total network", y = "Percent of nodes attacked",
       title = "Change in the distribution of blackout size by nodes attacked")  + 
  scale_x_continuous(labels=scales::percent) 
#ggsave(file.path(FiguresFolder, "BlackoutNodeDens1to15perc.pdf"))

PNodeDens %>%
  filter(NodesAttacked %in% targnodes) %>%
  mutate(  PercAttacked= fct_rev(as_factor(paste0(PercNum, "%"))))  %>%
  ggplot(aes(y = PercAttacked)) +
  geom_density_ridges(aes(x = GCfract, fill = Cascade), alpha = 0.5) +
  labs(x = "Reduction in GC size", y = "Percent of nodes attacked",
       title = "Change in the distribution of GC size by nodes attacked")  + 
  scale_x_continuous(labels=scales::percent) 
#ggsave(file.path(FiguresFolder, "GCNodeDens1to15perc.pdf"))

PNodeDens %>%
  group_by(Cascade) %>%
summarise(corre = cor(GCfract, Blackout))

PNodeDens %>%
  ggplot(aes(x= GCfract, Blackout, colour = Cascade ), alpha = 0.3) + geom_point() +
  coord_cartesian(xlim = c(0,1), ylim= c(0,0.8)) +
  labs(title = "Relationship between Blackout and Giant Component", 
       x = "Reduction in Giant Component size",
       y ="Blackout as a percentage of total network")
ggsave(file.path(FiguresFolder, "GCvsBlackoutNodes.pdf"))


PNodeDens %>%
  ggplot(aes(x= LoadDrop, Blackout, colour = Cascade ), alpha = 0.3) + geom_point() +
  labs(title = "Relationship between Blackout and Giant Component", 
       x = "Grid Loading",
       y ="Blackout as a percentage of total network")


SummaryofGC %>%
    ggplot(aes(x= PercNum, y = mLoad, colour = Cascade)) +geom_line() +
    geom_ribbon(aes(ymin=GL05, ymax=GL95, fill = Cascade), alpha = 0.3) +
  labs(title = "Mean Network Loading throughout grid attack", x = "Nodes attacked as percentage of grid", y = "Mean Network Load")
ggsave(file.path(FiguresFolder, "MLoad1to16Perc.pdf"))

```


#Edge collapse

Need to talk about what is being removed etc where does balance gen go?

```{r}
gc()
set.seed(1234)

Edges2remove<- ceiling(ecount(gbase)*0.15)

input <- c(TRUE,FALSE)
g <- PowerFlow(gbase, "FECK40")
  Edgesims <- input %>% map(~{ 
    MonteCarloAttack(g, 
                           simulations = 100,
                           AttackStrategy = RandomAttack,
                           Type = "Fixed",
                           MinMaxComp = 0.0, 
                           TotalAttackRounds = Edges2remove,
                           Target = "Edges",
                           CascadeMode = .x,
                           cores = 3)
    

    }
   ) %>% set_names(paste0("v.", input))


setwd(basewd)
saveRDS(Edgesims,"100simulationsRandomAttackto150Edges.rds")
#Edgesims <- readRDS("100simulationsRandomAttackto150Edges.rds")

SummaryofGCEdge <- Edgesims %>%
    modify_depth(., 1, keep, is.data.frame ) %>%
  flatten %>%
  bind_rows() %>% 
  SummariseMonteCarlo  %>%
  mutate(PercNum = NodesAttacked/1415)


EdgeCollapse <- rbind(SummaryofGCEdge%>%
  select(PercNum, mean, Cascade, GC05, GC95) %>% mutate(type = "Giant componant size reduction"),
SummaryofGCEdge %>% 
  select(PercNum, mPGfract, Cascade, PG05, PG95) %>% mutate(type = "Blackout size") %>%
  rename(mean = mPGfract, GC05 = PG05, GC95 = PG95)
) %>% mutate(Target = "Edge")



bind_rows(EdgeCollapse, NodeCollapse) %>%
    ggplot(aes(x= PercNum, y = mean, colour = Cascade)) +geom_line() +
    geom_ribbon(aes(ymin=GC05, ymax=GC95, fill = Cascade), alpha = 0.3) + 
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  facet_grid(Target~type) +
  labs(title = "Change in Giant Componant and Blackout size as nodes are attacked" , x = "Percent of elements attacked", y = "Performance drop")
ggsave(file.path(FiguresFolder, "NodeEdgeCollapse15perc.pdf"))



x=c(1:ecount(gbase))/ecount(gbase)
target=c(1:15)/100
TargEdges <- target %>% map_dbl(~which(abs(x-.x)==min(abs(x-.x))))

PEdgeDens <-  Edgesims %>%
    modify_depth(., 1, keep, is.data.frame ) %>%
  flatten %>%
  bind_rows() %>%
  mutate(PercNum = round(NodesAttacked*100/ecount(gbase)))

PEdgeDens %>%
  filter(NodesAttacked %in% TargEdges) %>%
  mutate(  PercAttacked= fct_rev(as_factor(paste0(PercNum, "%"))))  %>%
  ggplot(aes(y = PercAttacked)) +
  geom_density_ridges(aes(x = Blackout, fill = Cascade), alpha = 0.5) +
  labs(x = "Blackout size as Percentage of total network", y = "Percent of nodes attacked",
       title = "Change in the distribution of blackout size by edges attacked")  + 
  scale_x_continuous(labels=scales::percent) 

PEdgeDens %>%
  filter(NodesAttacked %in% TargEdges) %>%
  mutate(  PercAttacked= fct_rev(as_factor(paste0(PercNum, "%"))))  %>%
  ggplot(aes(y = PercAttacked)) +
  geom_density_ridges(aes(x = GCfract, fill = Cascade), alpha = 0.5) +
  labs(x = "Blackout size as Percentage of total network", y = "Percent of nodes attacked",
       title = "Change in the distribution of blackout size by edges attacked")  + 
  scale_x_continuous(labels=scales::percent) 

cor(PEdgeDens$GCfract, PEdgeDens$Blackout)

PEdgeDens %>%
  ggplot(aes(x= GCfract, Blackout, colour = Cascade ), alpha = 0.3) + geom_point()+
  coord_cartesian(xlim = c(0,1), ylim= c(0,0.8))


test <- bind_rows(PEdgeDens %>%
filter(NodesAttacked %in% TargEdges) %>%
  mutate(Target = "Edges"),
PNodeDens %>%
  filter(NodesAttacked %in% targnodes) %>%
  mutate(Target = "Nodes")
)%>%
#  filter(PercNum == 10) %>%
  select(GCfract, Blackout, Cascade, Target, PercNum) %>%
  gather(., key="Type", value = "value",GCfract, Blackout) %>%
  mutate(Type = ifelse(Type == "GCfract","Giant componant size reduction", "Blackout size"))
  

test %>% 
    filter(PercNum == 10) %>%
  ggplot(aes(x = value,  fill = Cascade)) +
  geom_density(alpha = 0.5)  +
    facet_grid(Target~Type) +
  scale_x_continuous(labels=scales::percent)  +
  coord_cartesian(ylim = c(0,15)) +
  labs(x = "Blackout size as Percentage of total network", y = "Percent of nodes attacked",
       title = "Change in the distribution of blackout size by edges attacked")
  ggsave(file.path(FiguresFolder, "NodeEdge15percDe
                   ns.pdf"))
  
  
  
 test   %>%
  mutate(  PercAttacked= fct_rev(as_factor(paste0(PercNum, "%"))))  %>%
  ggplot(aes(y = PercAttacked)) +
  geom_density_ridges(aes(x = value, fill = Cascade), alpha = 0.5)  + 
  scale_x_continuous(labels=scales::percent)  +
      facet_grid(Target~Type) +
  labs(x = "Performance drop", y = "Percent of elements attacked",
       title = "Change in the performance distribution as number of attacks increase") 
  ggsave(file.path(FiguresFolder, "NodeEdge15percDens4Way.pdf"))  

```


#Analysing worst collapse

```{r}

Analysims <- Nodesims
  
#Rank the different simulations by order of most extreme
CollapseRank <- BiggestCollapse(Analysims$v.FALSE$NetData, PowerGen)

#extract the simulation number of the most extreme collapse
ExtremeSimulation <- CollapseRank$Simulation[which.min(CollapseRank$PowerGen)]

#Find the nodes removed in the most extreme attack
ExtremeNodes <- Analysims$v.FALSE$AttackedNodes[[ExtremeSimulation]]

#Resimulate the attack to extract the details
FixedNodes <- quo(FixedStrategyAttack(g, ExtremeNodes ))
CheckCollapse <- AttackTheGrid(list(list(gbase)), FixedNodes, MinMaxComp = 0, TotalAttackRounds = length(ExtremeNodes), CascadeMode = TRUE) 

#not sure what to check now but there are two components and about 44 nodes have been lost
CheckCollapse[[31]][[1]] %>% components()

CheckCollapse[[31]][[1]] %>%
  get.vertex.attribute(name= "BalencedPower") %>% abs %>% sum(.)/2

#perhaps making a gif would help understand what has happened?

test <-  ExtractNetworkStats(CheckCollapse) 
 
ChangeInNet <- CheckCollapse %>% squash %>% map_dbl(~Net_Ability(.x,gbase))
a
 test %>%
   ggplot(aes(x=NodesAttacked, y = Blackout)) + geom_line()

 CreateCascadeGif(CheckCollapse)

 
 
```


```{r}

testgraph <- KNearestNodes(gbase, "ALVE4A", 2) %>% induced_subgraph(gbase, .)

  DeleteNodes <- RandomAttack(testgraph,Target = "Edges",Number = ecount(testgraph))
  FixedNodes <- quo(FixedStrategyAttack(g, DeleteNodes, Target = "Edges"))

Output <- AttackTheGrid(list(list(testgraph)), 
                                             FixedNodes, 
                                             MinMaxComp = 0, #
                                             TotalAttackRounds = 10, 
                                             CascadeMode =  TRUE)
giftest <- unlist(CheckCollapse, recursive = F)
 

CascadeList <- giftest


CreateCascadeGif(CheckCollapse)
 

```

#Load Level

Calculating the load level for the base case and looking at the distribution across lines

```{r}

g <- PowerFlow(gbase, "FECK40")

LoadAnalysis <- LoadLevel(g)



LL<- mean(LoadAnalysis$LineLoading[LoadAnalysis$Line.Limit!=100000])

1/LL

median(LoadAnalysis$LineLoading[LoadAnalysis$Line.Limit!=100000])

LoadAnalysis %>%
  filter(Line.Limit != 100000) %>%
  ggplot(aes(x= LineLoading)) + geom_histogram(aes(y = (..count..)/sum(..count..)), bins = 20) +
  labs(title = "Loading Level for base case profile", x = "Loading of maximum line limit as percent",
       y = "Percent of edges")+
  scale_x_continuous(labels=scales::percent, breaks = seq(0,1,0.1)) +
  scale_y_continuous(labels = scales::percent)+
  annotate("text", x = 0.7, y = 0.10, label = paste0("Mean Load Level ", round(LL*100), "%"), size = 10)+
  coord_cartesian(ylim = c(0,.15))

  ggsave(file.path(FiguresFolder, "LoadLevelHisto.pdf"))  

  
LoadAnalysis %>%
  mutate(LineLoading = ifelse(Line.Limit==100000, NA, LineLoading))  %>%
  #filter(Line.Limit != 100000) %>%
  ggplot(aes(x= LineLoading)) +geom_density()  +
  scale_x_log10()


E(g)$Loading <- get.edge.attribute(g, "Link.Limit")/abs(get.edge.attribute(g, "PowerFlow"))

g1<-g
E(g1)$AbsFlow <- abs(get.edge.attribute(g1, "PowerFlow"))

test <- data.frame(EntLim = EntropicDegree(g), 
                   EntLoad = EntropicDegree(g, value = "Loading"),
                   EntFlow = EntropicDegree(g1, value = "AbsFlow"))

#one third of rows removed due to non-finite values
test %>% gather%>%
  ggplot(aes(x= value, fill = key)) +
  geom_density(alpha = 0.5) +
  scale_x_log10()

```


#Who researched what equations
This code chunk is used to show the change from topological to extended topological
```{r}
TypeYear<- bind_rows(
data_frame(type = "Topo", year = c(2000,2002,2004,2004,2005,2007,2008,2006,2005,2007,2007,2004,2005,2009,2010,2009,2012,2007,2011,2004,2005)),

data_frame(type = "Extended", year = c(2011,2013,2008,2008,2009)),

data_frame(type = "Power Flow", year = c(2009,2010,2009,2007,2010,2010,2010,2011,2013,2010,2013,2014,2015,2011,2012,2012))
) %>%
  mutate(Type = ifelse(type == "Power Flow", "Extended", type),
         year = as.numeric(year))

TypeYear %>%
  ggplot(aes(x= year, fill = Type)) + geom_bar(position = "dodge") +
  labs(title = "Power grid as a complex network: Publication type by year")

ggsave(file.path(FiguresFolder, "PubTypePopularity.pdf"))

TypeYear %>% filter(type != "Extended") %>%
  ggplot(aes(x= year, fill = type)) + geom_bar(position = "dodge") +
  labs(title = "Power grid as a complex network: Publication type by year")


TypeYear %>%
  ggplot(aes(x= year, fill = Type)) + geom_freqpoly()

```


#Plots for the upgrade presentation

##SCALE FREE NETWORK AND POWER LAW PLOT
```{r}
setwd(basewd)
g <- sample_fitness_pl(1000, 500, 2, -1)
g <- delete.vertices(g, degree(g)==0)

components(g)

g <- delete.vertices(g, components(g)$membership!=which.max(components(g)$csize))


plot(g)
write_graph(g, "scale free.graphml" , "graphml")
g2 <- sample_fitness_pl(10000, 10000, Inf, -1)
g2 <- delete.vertices(g2, degree(g2)==0)

df <- data.frame(values =degree(g2), metric = "Degree") 

df%>%
ggPowerLaw() + 
  labs(title = "Power Law distribution")

      df2 <- df %>% filter(metric == 1)
      
      PL = df2$values %>% conpl$new(.)
      est = estimate_xmin(PL)
      PL$setXmin(est)
ggsave("PowerLawDistrib.pdf")

```

##LATTICE NETWORK and regular

```{r}
lat <- make_lattice(length = 5, dim = 2)

plot(lat)
write_graph(lat, "lattice.graphml" , "graphml")

random_lat <- sample_gnm(25, 40)
plot(random_lat)
write_graph(random_lat, "random_lattice.graphml" , "graphml")
```

##Uniform distribution

```{r}

data.frame(x = 1:20, y = rep(0.1, 20)) %>%
  ggplot(., aes(x= x, y = y)) +
  geom_col()+
  #geom_ribbon(aes(ymin = 0, ymax = y)) +
  coord_cartesian(xlim = c(0,20), ylim = c(0,0.15)) +
  labs(title = "Loading per line across network", x = "Line ID") +
  scale_y_continuous(name = paste0("Percentage Loading " ), labels = expression(frac(1,alpha)), breaks = 0.1)
ggsave("Uniform_Loading.pdf")

```

